\documentclass[margin,line]{res}

\usepackage{changepage}
\usepackage{xcolor}

\usepackage[greek, english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
%\usepackage{titlesec}
\usepackage{fontspec}
\usepackage[Latin,Greek]{ucharclasses}

\newfontfamily\substitutefont{CMU Serif}
\setTransitionsForGreek{\begingroup\substitutefont}{\endgroup}


\newcommand{\g}{\textgreek}
\newcommand{\ver}{\vspace*{-2.7mm}}
\renewcommand{\baselinestretch}{1.0}
%\renewcommand{\baselineskip}{1.5in}

\oddsidemargin -0.7in
\evensidemargin -.7in
\textwidth=6.2in
\textheight=690pt
\voffset=-0.4in
\hoffset=1.4in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\definecolor{urlblue}{HTML}{0000EE}

\usepackage{orcidlink}

\begin{document}

\name{ Nikolaos Ignatiadis \orcidlink{0000-0001-7767-2583} --- CV  \hspace{17em} {\normalfont \textit{Last update: \today}}\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Details}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Columbia University             & {Telephone:}  +1 (650) 656-0855 \\
Department of Statistics   & {E-mail:}    ignat@stanford.edu \\
1255 Amsterdam Ave, &  {Website:} \href{https://nignatiadis.github.io/}{https://nignatiadis.github.io/}\\
New York, NY 10027, USA  & {Google Scholar:} \href{https://scholar.google.com/citations?user=KH3jpkoAAAAJ}{user=KH3jpkoAAAAJ} \\
\end{tabular}



\section{\sc Research Interests}
I am interested in the development of interpretable statistical methods, accompanied by robust software implementations, for the analysis of datasets generated from modern, high-throughput technologies. From a statistical perspective, this interest encompasses Empirical Bayes analysis, causal inference, multiple testing and statistics in the presence of contextual side-information.

\section{\sc Academic Employment}
{\bf Department of Statistics and Data Science Institute, University of Chicago} \hfill Chicago, USA\\
\vspace*{-.14in}
\begin{list2}
\item Assistant Professor \hfill Beginning 07/2023
\end{list2}

{\bf Department of Statistics, Columbia University} \hfill New York, USA\\
\vspace*{-.14in}
\begin{list2}
\item Postdoctoral Research Scientist \hfill 09/2022 - 06/2023
\end{list2}



\section{\sc Education}
{\bf Stanford University} \hfill Stanford, California, USA\\
%{\em Department of Statistics}
\vspace*{-.14in}
\begin{list2}
\item
\textbf{Ph.D., Statistics}  (GPA 4.24) \hfill  09/2016 -- 06/2022\\
Thesis advisor: Stefan Wager\\
Thesis title: Nonparametric perspectives on empirical Bayes.
\item \textbf{M.S., Statistics}
\end{list2}

\vspace*{-2.5mm}
{\bf {Heidelberg University}} \hfill  {Heidelberg, Germany}\\
\vspace*{-.14in}
\begin{list2}
\item \textbf{M.Sc.,  Scientific Computing}, Grade 1.0 \hfill 2015 - 2016\\
Thesis advisors: Wolfgang Huber and Enno Mammen
\item \textbf{B.Sc., Mathematics}, Grade 1.0 with \emph{distinction} \hfill 2011 - 2015\\
Thesis advisors: Wolfgang Huber and Rainer Dahlhaus
\item \textbf{B.Sc., Molecular Biotechnology}, Grade 1.0 \hfill 2010 - 2013
\end{list2}


\section{\sc Awards and Fellowships }
\textbf{Jerome H. Friedman Applied Statistics Dissertation Award} \hfill 2022\\
For developing methodology that uses side information for increased power in multiple testing problems and for developing approaches to inference in empirical Bayes problems.\\
\textbf{Ric Weiland Graduate Fellowship  in the Humanities \& Sciences } \hfill 2020 - 2021\\
This fellowship is awarded to exceptional rising fourth year doctoral candidates in the humanities, social sciences, mathematics, and
statistics upon departmental or programmatic nomination.\\
\textbf{Departmental Teaching Assistant Award}, Statistics Department, Stanford  \hfill  2018\\
\textbf{iGEM Grand Prize Winner \& Best Foundational Advance} \hfill  2013 \\
The International Genetically Engineered Machine competition with Team Heidelberg at MIT.\\
\textbf{Deutschlandstipendium}, Heidelberg University, Germany \hfill 2011 - 2013\\
This scholarship is awarded to talented and high-achieving students at public and state recognised institutions of higher education in Germany and is supported by the German Federal Government.\\
\textbf{Bronze medal at the International Biology Olympiad}, Changwon, South Korea \hfill 2010

\section{\sc Journal Publications}
\begin{list1}

\item[1.]
Nikolaos Ignatiadis, Stefan Wager (2022).
\textbf{Rejoinder: Confidence Intervals for Nonparametric Empirical Bayes Analysis.}
Journal of the American Statistical Association, Theory and Methods, 117(539), 1192-1199.

\item[2.]
Nikolaos Ignatiadis, Stefan Wager (2022).
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis.}
Journal of the American Statistical Association, Theory and Methods, 117(539), 1149-1166.

\item[3.]
Nikolaos Ignatiadis, Sujayam Saha, Dennis L. Sun, Omkar Muralidharan (2021).
\textbf{Empirical Bayes mean estimation with nonparametric errors via order statistic regression on replicated data.}
Journal of the American Statistical Association, Theory and Methods (forthcoming).

\item[4.]
Nikolaos Ignatiadis, Wolfgang Huber (2021).
\textbf{Covariate powered cross-weighted multiple testing.}
Journal of the Royal Statistical Society: Series B (JRSS-B), 83(4), 720-751.

\item[5.]
Loukia Karacosta, Benedict Anchang, Nikolaos Ignatiadis, Samuel Kimmey, Jalen Benson, Joseph Shrager, Robert Tibshirani, Sean Bendall, Sylvia K. Plevritis (2019).
\textbf{Mapping lung cancer epithelial-mesenchymal transition states and trajectories with single-cell resolution.}
Nature communications, 10, 5887.

\item[6.]
Nikolaos Ignatiadis, Bernd Klaus, Judith Zaugg, Wolfgang Huber (2016).
\textbf{Data-driven hypothesis weighting increases detection power in genome-scale multiple testing.}
Nature methods, 13(7), 577-580.

\item[7.]
Ralf Beer, Konrad Herbst, Nikolaos Ignatiadis, Ilia Kats, Lorenz Adlung, Hannah Meyer, Dominik Niopek, Tania Christiansen, Fanny Georgi, Nils Kurzawa, Johanna Meichsner, Sophie Rabe, Anja Riedel, Joshua Sachs, Julia Schessner, Florian Schmidt, Philipp Walch, Katharina Niopek, Tim Heinemann, Roland Eils, Barbara Di Ventura (2014).
\textbf{Creating functional engineered variants of the single-module non-ribosomal peptide synthetase IndC by T domain exchange.}
Molecular BioSystems, 10(7), 1709-1718.

\end{list1}

\section{\sc Conference proceedings}
\begin{list1}

\item[8.]
Stephen Pfohl, Yizhe Xu, Agata Foryciarz, Nikolaos Ignatiadis, Julian Genkins, Nigam H. Shah (2022).
\textbf{Net benefit, calibration, threshold selection, and training objectives for algorithmic fairness in healthcare.}
ACM Conference on Fairness, Accountability, and Transparency (FAccT'22).

\item[9.]
Nikolaos Ignatiadis, Stefan Wager (2019).
\textbf{Covariate-Powered Empirical Bayes Estimation.}
Advances in Neural Information Processing Systems 32 (NeurIPS 2019).

\end{list1}

\section{\sc Book chapters}
\begin{list1}

\item[10.]
Yizhe Xu, Nikolaos Ignatiadis, Erik Sverdrup, Scott Fleming, Stefan Wager, Nigam H. Shah (2023).
\textbf{Treatment Heterogeneity with Survival Outcomes.}
Book chapter in: Handbook of Matching and Weighting Adjustments for Causal Inference. Edited by José R. Zubizaretta, Elizabeth A. Stuart, Dylan S. Small, and Paul R. Rosenbaum. Chapman and Hall / CRC Press.

\end{list1}

\section{\sc Preprints}
\begin{list1}

\item[11.]
Nikolaos Ignatiadis, Bodhisattva Sen (2023).
\textbf{Empirical partially Bayes multiple testing and compound χ² decisions.}
Working paper.

\item[12.]
Nikolaos Ignatiadis, Ruodu Wang, Aaditya Ramdas (2022).
\textbf{E-values as unnormalized weights in multiple testing.}
Working paper.

\item[13.]
Dean Eckles, Nikolaos Ignatiadis, Stefan Wager, Han Wu (2022).
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs.}
Working paper.

\item[14.]
Nikolaos Ignatiadis, Panagiotis Lolas (2021).
\textbf{σ-Ridge: group-regularized ridge regression via empirical Bayes noise level cross-validation.}
Working paper.

\end{list1}


\section{\sc Invited discussions}
\textbf{International Seminar on Selective Inference (ISSI)} \hfill December 2020\\
Discussant of the talk `Clipper: p-value-free FDR control on high-throughput data from two conditions'
by Prof. Jingyi Jessica Li.



\section{\sc Peer Review}

\textbf{Statistics journals}\\
Annals of Statistics (AoS),
Bernoulli,
Biometrical Journal,
Biometrics,
Biometrika,
Electronic Journal of Statistics (EJS),
Journal of the American Statistical Association: Theory \& Methods (JASA T\&M),
Journal of Business \& Economic Statistics (JBES),
Journal of Causal Inference (JCI),
Journal of Computational and Graphical Statistics (JCGS),
Journal of the Royal Statistical Society--Series B (JRSS-B),
Journal of Statistical Software (JSS),
Statistical Papers,
Statistical Science

\ver

\textbf{Other journals}\\
Bioinformatics,
Bioinformatics Advances,
BMC Medical Research Methodology,
Journal of Cell Science,
Management Science,
Nature Protocols,
Operations Research,
PeerJ

\ver
\textbf{Conferences}\\
AISTATS (2021),
NeurIPS (2021, 2022),
ICLR (2022)

\section{\sc Software}
{\bf R packages} in Bioconductor:
\begin{list2}
\item \href{https://bioconductor.org/packages/IHW}{{\color{urlblue} IHW}}:  Independent Hypothesis Weighting for multiple testing with side-information.
\item \href{https://bioconductor.org/packages/IHWpaper}{{\color{urlblue} IHWpaper}}: Companion to the IHW package facilitating reproducibility.
\end{list2}
{\bf Julia packages} in the official registry:
\begin{list2}
\item \href{https://github.com/nignatiadis/Aurora.jl}{{\color{urlblue} Aurora.jl}}: Empirical Bayes mean estimation with nonparametric errors on replicated data.
\item \href{https://github.com/nignatiadis/Empirikos.jl}{{\color{urlblue} Empirikos.jl}}: Nonparametric empirical Bayes confidence intervals.
\item \href{https://github.com/nignatiadis/RegressionDiscontinuity.jl}{{\color{urlblue}  RegressionDiscontinuity.jl}}: Basic functionality for analyzing sharp regression discontinuity designs.
\item \href{https://github.com/nignatiadis/SigmaRidgeRegression.jl}{{\color{urlblue} SigmaRidgeRegression.jl}}: $\sigma$-Ridge for regression with features that can be partitioned into groups.
\item \href{https://github.com/nignatiadis/SmoothingSplines.jl}{{\color{urlblue} SmoothingSplines.jl}}: Nonparametric regression using smoothing splines.
\item Contributions to Distributions.jl, GLM.jl, MultipleTesting.jl and others.
\end{list2}


\section{\sc Industry experience}
\textbf{Google AdsMetrics}, Mountain View, USA \hfill Summer 2019\\
Data science intern with Omkar Muralidharan, Sujayam Saha and Dennis L. Sun.


\section{\sc Research appointments}
{\bf Biomedical Informatics},  Stanford, California, USA \hfill 2021 - 2022\\
Research assistant in the group of Prof. Nigam Shah funded by the NHLBI R01 grant `Applying statistical learning tools to personalize cardiovascular treatment'.\\
{\bf Statistics Department},  Stanford, California, USA \hfill 2017 - 2021\\
Research assistant with Prof. Stefan Wager working on empirical Bayes and causal inference problems.
{\bf European Molecular Biology Laboratory},  Heidelberg, Germany \hfill 2014 - 2016\\
Research assistant in the group of Dr. Wolfgang Huber.



\section{\sc Teaching}
\textbf{Instructor} at Columbia University\\
GR8201: Topics in Theoretical Statistics, Empirical Bayes (jointly with Bodhisattva Sen) \hfill Spring 2023

\ver

\textbf{Instructor} at Stanford University\\
STATS 302: Applied Statistics Ph.D. Qualifying Exam Workshop. \hfill Summer 2020

\ver
\textbf{Teaching Assistant (TA)} at Stanford University\\
STATS 315B: Modern Applied Statistics: Data Mining. \hfill Spring 2021\\
STATS 361: Causal Inference. \hfill Spring 2020\\
STATS 305B: Applied Statistics II. \hfill Winter 2020\\
STATS 315A: Modern Applied Statistics: Learning. \hfill Winter 2019\\
STATS 300A: Theory of Statistics I. \hfill Fall 2018\\
STATS 366 (BIOS 221): Modern Statistics for Modern Biology. \hfill Summer 2017 \& 2018, Fall 2019\\
STATS 218: Introduction to Stochastic Processes II. \hfill Spring 2018\\
STATS 290: Computing for Data Science. \hfill Winter 2018\\
STATS 305A: Introduction to Statistical Modeling. \hfill Fall 2017\\
STATS 191: Introduction to Applied Statistics. \hfill Winter 2017\\
STATS 141 (BIOS 141): Biostatistics.\hfill Fall 2016

\ver
\textbf{Trainer} at EMBL (European Molecular Biology Laboratory)\\
Introductory Course: Statistical Bioinformatics using R and Bioconductor \hfill October 2015

\section{\sc Talks and Presentations}
\begin{adjustwidth*}{0pt}{0pt}
 
\textbf{Empirical partially Bayes multiple testing and compound χ² decisions} \\
2023 Berkeley–Columbia Meeting in Engineering and Statistics, Columbia University \\
New York, NY, USA, April 2023
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis} \\
Seminar at Department of Statistics and Data Science, Yale University \\
New Haven, CT, USA, November 2022
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Econometrics Colloquium at the Economics Department, Columbia University \\
New York, NY, USA, November 2022
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis} \\
Statistics Department Seminar at Athens University of Economics and Business (AUEB) \\
Virtual, October 2022
 \\
\textbf{Covariate-Powered Empirical Bayes Estimation} \\
Seminar (student seminar series) at the Department of Statistics, Columbia University \\
New York, NY, USA, September 2022
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Second Congress of Greek Mathematicians (SCGM) \\
Virtual, July 2022
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis} \\
JASA Theory and Methods Invited Session at the Joint Statistical Meetings (JSM) \\
Washington, DC, USA, June 2022
 \\
\textbf{Covariate-powered empirical Bayes estimation} \\
New ideas in empirical Bayes at the 5th International Conference on Econometrics and Statistics (EcoSta 2022) \\
Virtual, June 2022
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Methodological innovations for challenges in health policy and clinical care at the 2022 American Causal Inference Conference \\
Berkeley, CA, USA, May 2022
 \\
\textbf{Empirical Bayes Mean Estimation With Nonparametric Errors Via Order Statistic Regression on Replicated Data} \\
Statistics Seminar at the Department of Statistics, UC Davis \\
Davis, CA, USA, April 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Statistics and Data Science Seminar at the Department of Statistics and Data Science, Carnegie Mellon University \\
Virtual, February 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Statistics Seminar at the Department of Statistics, University of British Columbia \\
Virtual, February 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Statistics Seminar at the Department of Statistics and Data Science, Wharton School of the University of Pennsylvania \\
Virtual, February 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Seminar at the Department of Decision Sciences, Bocconi University \\
Milano, Italy, February 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Statistics Seminar at the Department of Statistics, UC Davis \\
Virtual, January 2022
 \\
\textbf{Confidence intervals for nonparametric empirical Bayes analysis and an application to regression discontinuity designs} \\
Statistics Seminar at the Department of Statistics, UCLA \\
Virtual, January 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Seminar at the Data Science Institute, University of Chicago \\
Chicago, Illinois, USA, January 2022
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis and an Application to Regression Discontinuity Designs} \\
Seminar at the Department of Statistics and Actuarial Science, University of Waterloo \\
Virtual, January 2022
 \\
\textbf{Nonparametric Empirical Bayes Inference} \\
Statistics Seminar at the Department of Statistics, Columbia University \\
Virtual, January 2022
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis and an Application to the Regression Discontinuity Design} \\
ACMS Colloquium at Department of Applied and Computational Mathematics and Statistics,  University of Notre Dame \\
Notre Dame, Indiana, USA, December 2021
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis} \\
Advances in Empirical Bayes Methodology at the International Conference on Computational and Methodological Statistics (CMStatistics) \\
Virtual, December 2021
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Fourth Annual Berkeley-Stanford Econometrics Jamboree at UC Berkeley \\
Berkeley, CA, USA, November 2021
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Causal Science Conference at Stanford University \\
Stanford, USA, November 2021
 \\
\textbf{Noise-Induced Randomization in Regression Discontinuity Designs} \\
Causal Inference When Resources Are Limited at the Joint Statistical Meetings (JSM) \\
Virtual, August 2021
 \\
\textbf{Confidence Intervals for Nonparametric Empirical Bayes Analysis} \\
International Seminar on Selective Inference (ISSI) \\
Virtual, April 2021
 \\
\textbf{σ-Ridge: group regularized ridge regression via empirical Bayes noise level cross-validation} \\
Statistics Seminar at Vrije Universiteit (VU) Amsterdam campus \\
Virtual, April 2021
 \\
\textbf{Discussion of 'Clipper: p-value-free FDR control on high-throughput data from two conditions'} \\
Discussant at the International Seminar on Selective Inference (ISSI) \\
Virtual, December 2020
 \\
\textbf{Bias-Aware Confidence Intervals for Empirical Bayes Analysis} \\
Causality in Statistical Data Science at the Joint Statistical Meetings (JSM) \\
Virtual, August 2020
 \\
\textbf{Covariate-Powered Empirical Bayes Estimation} \\
Blue Seminar at the European Molecular Biology Laboratory (EMBL) \\
Heidelberg, Germany, January 2020
 \\
\textbf{Covariate-Powered Empirical Bayes Estimation} \\
11th International Conference on Multiple Comparison Procedures at the National Taiwan University (NTU) \\
Taipei, Taiwan, December 2019
 \\
\textbf{Bias-Aware Confidence Intervals for Empirical Bayes Analysis} \\
Atlantic Causal Inference Conference at McGill University \\
Montreal, Canada, May 2019
 \\
\textbf{Covariate powered cross-weighted multiple testing} \\
Statistics Industrial Affiliates Conference at Stanford University \\
Stanford, CA, USA, February 2019
 \\
\textbf{Covariate-powered cross-weighted multiple testing with FDR Control} \\
Workshop in Post-selection Inference and Multiple Testing at the Institut de Mathématiques de Toulouse \\
Toulouse, France, February 2018
 \\
\textbf{MultipleTesting.jl: Simultaneous Statistical Inference in Julia} \\
Lightning talk at JuliaCon \\
Berkeley, CA, USA, June 2017
 \\
\textbf{Data-driven hypothesis weighting increases detection power in genome-scale multiple testing} \\
Genome Biology Seminar at the European Molecular Biology Laboratory (EMBL) \\
Heidelberg, Germany, July 2016

\end{adjustwidth*}
\end{resume}
\end{document}
